Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-09-08 ms.tex
made edits requested by referee through section 4.

The atmospheres of L-type stars and brown dwarfs (1300~K $\lesssim$ {\teff} $\lesssim$ 2200~K; \citealt{2015ApJ...810..158F}) are sufficiently cool that species of mineral and metal condensates form spontaneously in their atmospheres \citep{1996A&A...305L...1T,2010ApJ...716.1060V}.
In addition to influencing spectral energy distributions (e.g., \citealt{2001ApJ...556..357A,2008ApJ...674..451B}) and photospheric chemistry (e.g., \citealt{2000ApJ...531..438B}), condensates can coalesce into large-scale cloud and haze structures \citep{1989ApJ...338..314L,2001ApJ...556..872A,2014Natur.505..654C}.
These structures may produce rotationally-modulated brightness variations (e.g., \citealt{2012ApJ...750..105R}) and long-term variations from differential rotation and/or cloud structure evolution (e.g., \citealt{2009ApJ...701.1534A,2013A&A...555L...5G,2016ApJ...826....8Y}). Evidence of cloud-driven variability extends to the cooler T dwarfs (e.g., \citealt{2009ApJ...701.1534A,2012ApJ...760L..31B,2015ApJ...799..154M}), virtually all L dwarfs and most T dwarfs likely have cloud deck heterogeneities leading to infrared flux variations $\gtrsim$0.2\% in amplitude \citep{2015ApJ...799..154M}. Clouds and hazes are important constituents of exoplanetary atmospheres as well (e.g., \citealt{2011ApJ...733...65B,2014Natur.505...69K,2016Natur.529...59S}).

Multi-wavelength monitoring of low-temperature stars and brown dwarfs allows for the measurement of cloud vertical structure and composition, as gray grain scattering opacity competes with strongly wavelength-dependent molecular gas opacity. The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A} and amplitude spectra have been shown to vary with effective temperature ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) and surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
Wavelength-dependent phase variations in lightcurves have also been observed \citep{2012ApJ...760L..31B,2013ApJ...778L..10B,2016ApJ...826....8Y}.
Since different wavelengths sample different photospheric depths in the highly structured spectra of L and T dwarfs, these phase variations have been interpreted as arising from the relative motion of distinct cloud layers or deep thermal pulsations. Deep thermal pulsations occur on longer timescales ($\sim$ 100 hr for an example T-dwarf model) but may interact with clouds to produce shorter timescale variability \citep{2014ApJ...785..158R}.

@@

Ground-based Multi-Object Spectroscopy (MOS) with a multi-object or long slit spectrograph, in which reference stars are simultaneously observed to correct for telluric effects can significantly improve the precision of ground-based spectro-photometry (e.g., \citealt{bean10,bean2013,gibson13clouds,stevenson2016hatp26}). \citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star CoRoT-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby reference star in a wide and long (3$\arcsec \times 60 \arcsec$) slit.
This was sufficient to infer the presence of a cloud/haze layer or disfavor TiO/VO absorption in CoRoT-1b via transmission spectroscopy. A similar investigation of the disintegrating rocky exoplanet KIC 12557548b  enabled the characterization of the grain properties of its tidal debris tail \citep{2016ApJ...826..156S}. In a parallel effort, \citet{2014ApJ...785...48B} obtained $<$0.5\% per-band relative precision across the 1--2.5~$\mu$m band with IRTF/SpeX for the variable T dwarf Luhman 16B, by simultaneously observing it and its L dwarf companion. These studies demonstrate that high-precision, near-infrared spectral monitoring observations can be achieved from the ground.

@@

2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to youth and/or thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G,2016ApJ...833...96L} and Li absorption \citep{2008ApJ...686..528L}.
This source is a photometric variable with a period of 4.2$\pm$0.1~hr \citep{2015ApJ...799..154M} and $v\sin{i}$ = 28.85$\pm$0.16~{\kms}  \citep{2010ApJ...723..684B}, suggesting a near equator-on orientation.  \citet{2015ApJ...798L..13Y} measured 1--3\% spectral variability with $HST$/WFC3 over 1.1--1.6~$\micron$, with greater variabilty at shorter wavelengths.
There are three suitably bright reference stars within 40$\arcsec$ for relative calibration visible in Figure \ref{fig:images}. We chose 2MASS~J18212622+1414064 (visible in Figure~\ref{fig:images}) with $H$=12.0 at 32$\arcsec$ separation for our monitoring observations.

@@

The 2D images were rectified so that the X coordinates of all background spectra corresponded to the same wavelength.
This was achieved by selecting a reference row between the sources and then cross-correlating this reference spectrum with all other illuminated detector rows.
A third order polynomial was fit to the cross correlation peaks (masking out the sources) to determine a one dimensional smooth X (spectral) shift solution as a function of Y (spatial) position  \citep{2016ApJ...826..156S}.
Once the 2D spectral images were rectified, the background is subtracted along the Y (spatial) direction with a 4th order polynomial.
The reduction software is available online\footnote{https://github.com/eas342/spectral\_pipeline\_and\_scripts}.

We obtained ThAr arc lamp spectra, dark frames and flat field data for calibration.
The ThAr data is taken for wavelength calibration with the 0.3$\arcsec\times60\arcsec$ slit since it has a resolving power high enough to separate the ThAr lines and identify them.
This wavelength calibration data is taken at the very beginning and very end of the sequence to ensure the 3$\arcsec \times 60 \arcsec$ slit is unmoved during the rest of the calibration and science data.
Dark frames are taken with the same exposure time as the science images and with the order sorting filter set to the closed position.
We take flat field field data with an incandescent lamp to correct for high frequency, pixel-to-pixel variations.
For {\sha}, we used a combination of the flat-field lamp and a sky frame to construct a pixel response map, removing large-scale ($\gtrsim$ 30 pixels) structure with low order polynomial fits along spatial and spectral axes, and normalizing to the median response spectrum. 
To correct for instrument flexure, we cross-correlated the sky frame with each science image to measure linear spatial shifts, which were $\pm$5~pixels or 0.5\arcsec\ for \sha\ and $\pm$1.5~pixels or 0.15\arcsec\ for \shb.
These shifts were used to apply a custom flat field for every image.
For {\shb}, we did not have sufficient sky frames so we used our incandescent lamp image for both flat fielding and flexure analysis.

>>>>

The atmospheres of L-type stars and brown dwarfs (1300~K $\lesssim$ {\teff} $\lesssim$ 2200~K; \citealt{2015ApJ...810..158F}) are sufficiently cool that species of mineral and metal condensates form spontaneously in their atmospheres \citep{1996A&A...305L...1T,2010ApJ...716.1060V}.
In addition to influencing spectral energy distributions (e.g., \citealt{2001ApJ...556..357A,2008ApJ...674..451B}) and photospheric chemistry (e.g., \citealt{2000ApJ...531..438B}), condensates can coalesce into large-scale cloud and haze structures \citep{1989ApJ...338..314L,2001ApJ...556..872A,2014Natur.505..654C}.
These structures may produce rotationally-modulated brightness variations (e.g., \citealt{2012ApJ...750..105R}) and long-term variations from differential rotation and/or cloud structure evolution (e.g., \citealt{2009ApJ...701.1534A,2013A&A...555L...5G,2016ApJ...826....8Y}). Evidence of cloud-driven variability extends to the cooler T dwarfs (e.g., \citealt{2009ApJ...701.1534A,2012ApJ...760L..31B,2015ApJ...799..154M})\textbf{; virtually} all L dwarfs and most T dwarfs likely have cloud deck heterogeneities leading to infrared flux variations $\gtrsim$0.2\% in amplitude \citep{2015ApJ...799..154M}. Clouds and hazes are important constituents of exoplanetary atmospheres as well (e.g., \citealt{2011ApJ...733...65B,2014Natur.505...69K,2016Natur.529...59S}).

Multi-wavelength monitoring of low-temperature stars and brown dwarfs allows for the measurement of cloud vertical structure and composition, as gray grain scattering opacity competes with strongly wavelength-dependent molecular gas opacity. The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A}\textbf{, and} amplitude spectra have been shown to vary with effective temperature ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) and surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
Wavelength-dependent phase variations in lightcurves have also been observed \citep{2012ApJ...760L..31B,2013ApJ...778L..10B,2016ApJ...826....8Y}.
Since different wavelengths sample different photospheric depths in the highly structured spectra of L and T dwarfs, these phase variations have been interpreted as arising from the relative motion of distinct cloud layers or deep thermal pulsations. Deep thermal pulsations occur on longer timescales ($\sim$ 100 hr for an example T-dwarf model) but may interact with clouds to produce shorter timescale variability \citep{2014ApJ...785..158R}.

@@

Ground-based Multi-Object Spectroscopy (MOS) with a multi-object or long slit spectrograph, in which reference stars are simultaneously observed to correct for telluric effects can significantly improve the precision of ground-based spectro-photometry (e.g., \citealt{bean10,bean2013,gibson13clouds,stevenson2016hatp26}). \citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star CoRoT-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby reference star in a wide and long (3$\arcsec \times 60 \arcsec$) slit.
This was sufficient to infer the presence of a cloud/haze layer or disfavor TiO/VO absorption in CoRoT-1b via transmission spectroscopy. A similar investigation of the disintegrating rocky exoplanet KIC 12557548b  enabled the characterization of the grain properties of its tidal debris tail \citep{2016ApJ...826..156S}. In a parallel effort, \citet{2014ApJ...785...48B} obtained $<$0.5\% per-band relative precision across the 1--2.5~$\mu$m band with IRTF/SpeX for the variable T dwarf Luhman 16B, by simultaneously observing \textbf{Luhman 16A, a physically associated L dwarf companion nearby on the sky}. These studies demonstrate that high-precision, near-infrared spectral monitoring observations can be achieved from the ground.

@@

2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to youth and/or thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G,2016ApJ...833...96L} and Li absorption \citep{2008ApJ...686..528L}.
This source is a photometric variable with a period of 4.2$\pm$0.1~hr \citep{2015ApJ...799..154M} and $v\sin{i}$ = 28.85$\pm$0.16~{\kms}  \citep{2010ApJ...723..684B}, suggesting a near equator-on orientation.  \citet{2015ApJ...798L..13Y} measured 1--3\% spectral variability with $HST$/WFC3 over 1.1--1.6~$\micron$, with greater variabilty at shorter wavelengths.
There are three suitably bright reference stars within 40$\arcsec$ for relative calibration visible in Figure \ref{fig:images}.
We chose 2MASS~J18212622+1414064 (visible in Figure~\ref{fig:images}) with $H$=12.0 at 32$\arcsec$ separation for our monitoring observations \textbf{because this configuration minimized the amount of light entering the slit from the nearby visual companion to the north of our target.
However, we expect that another configuration with the reference star to the southwest could achieve similar spectro-photometric precision.}

@@

The 2D \textbf{prism} images\textbf{, which have a dispersion direction approximately along the X direction and spatial direction approximately along the Y direction,} were rectified so that the X coordinates of all background spectra corresponded to the same wavelength.
This was achieved by selecting a reference row between the sources and then cross-correlating this reference spectrum with all other illuminated detector rows.
A third order polynomial was fit to the cross correlation peaks (masking out the sources) to determine a one dimensional smooth X (spectral) shift solution as a function of Y (spatial) position  \citep{2016ApJ...826..156S}.
Once the 2D spectral images were rectified, the background is subtracted along the Y (spatial) direction with a 4th order polynomial.
The reduction software is available online\footnote{https://github.com/eas342/spectral\_pipeline\_and\_scripts}.

We obtained ThAr arc lamp spectra, dark frames and flat field data for calibration.
The ThAr data is taken for wavelength calibration with the 0.3$\arcsec\times60\arcsec$ slit since it has a resolving power high enough to separate the ThAr lines and identify them.
This wavelength calibration data is taken at the very beginning and very end of the sequence to ensure the 3$\arcsec \times 60 \arcsec$ slit is unmoved during the rest of the calibration and science data.
Dark frames are taken with the same exposure time as the science images and with the order sorting filter set to the closed position.
We \textbf{took} flat field field data with an incandescent lamp to correct for high frequency, pixel-to-pixel variations.
For {\sha}, we used a combination of the flat-field lamp and a sky frame to construct a pixel response map, removing large-scale ($\gtrsim$ 30 pixels) structure with low order polynomial fits along spatial and spectral axes, and normalizing to the median response spectrum. 
To correct for instrument flexure, we cross-correlated the sky frame with each science image to measure linear spatial shifts, which were $\pm$5~pixels or 0.5\arcsec\ for \sha\ and $\pm$1.5~pixels or 0.15\arcsec\ for \shb.
These shifts were used to apply a custom flat field for every image\textbf{, while shifting the sky flat (with pixel-to-pixel response removed) and maintaining the position of the pixel-to-pixel flat}.
For {\shb}, we did not have sufficient sky frames so we used our incandescent lamp image for both flat fielding and flexure analysis.
